Model Estimation

### 2019-01-09 manuscript.Rnw
WIP

tracts@data <-  tbl_df(tracts@data) %>%
  dplyr::transmute(
    geoid = GEOID,
    county_fips = substr(GEOID, 3, 5),
    borough = case_when(
      county_fips == "081" ~ "Queens",
      county_fips == "047" ~ "Brooklyn",
      county_fips == "061" ~ "Manhattan",
      county_fips == "005" ~ "Bronx",
      county_fips == "085" ~ "Staten Island",
      TRUE ~ as.character(NA)
    ),
    obesity = OBESITY,
    physact = 100 - Phys_Act,
    log_obesity = log(OBESITY),
    log_physact = log(100 - Phys_Act),
    density = Pop_Density,
    fulltime = FulltimeWork, college = CollegeDeg,
    single = Single_Percent,
    black = PctBlack, asian = PctAsian, hispanic = PctHispanic,
    other = PctNative + PctPacific,
    Pct0to17, Pct18to29, Pct65plus,
    Income1, Income2, Income3, Income4, Income5, Income6,
    Income7, Income8, Income9, Income10
  )
@

@@

<<tractsdata, results="asis", message=FALSE, warning=FALSE, cache=FALSE>>=
tracts_data_index <- data_frame(
  variable =  c(
    "obesity", "physact", "density", "fulltime", "college", "single", 
    "Pct0to17", "Pct18to29",  "Pct65plus", "black", "asian", "hispanic", 
    "other")
  ) %>% mutate(order = row_number())

tract_summary <- tracts@data %>%
  dplyr::select(obesity:Pct65plus) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  inner_join(tracts_data_index) %>%
  arrange(order) %>%
  mutate(
    variable = c(
      "Obesity Rate", "Physical Activity Rate",
      "Density: population per square mile",
      "Full-time workers", "College-educated", 
      "Single Adults", "Share of children (0-17)", "Share of young adults (18-29)", 
      "Share of seniors (65+)", "Black population share", "Asian population share", 
      "Hispanic population share", "Other Minorities")
  ) %>%
  dplyr::select(-order)

@@

We predict the rate of physical activity ($y$) in a census tract as a
function of the tract's sociodemographic characteristics and choice-based
accessibility to parks with a semi-log specification:
\begin{equation}\label{eq:themodel}
\log(y_i) = f(\vect{x}_i, CS_i, g(W, \mathit{Obesity}, \vect{X}))
\end{equation}
<<base_formula>>=
base_formula <- formula(
  ~ log(density) +
    fulltime + college + single +
    Pct0to17 + Pct18to29 + Pct65plus + # need to leave out a category for collinearity
    black + asian + hispanic + other)

termnames <- c("log(density)" , "Full-time workers", "College-educated", 
               "Single Adults", "Share of children (0-17)", "Share of young adults (18-29)", 
               "Share of seniors (65+)", "Black population share", "Asian population share", 
               "Hispanic population share", "Other Minorities")
@
where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
$CS_i$ is a choice-based
accessibility measure for the tract computed from Equation \ref{eq:cs} and
$g(W, \vect{y}, X)$
represents the impact of spatial neighborhood effects on the outcome.

@@

<<distances, warning=FALSE>>=
# calculate centroids of tracts and parks

parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

@@

<<logsum_betas>>=
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-0.42, 1.0)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.42, 1.0, 0.1)),
    access_ls = (access_ls - mean(access_ls) )/ sd(access_ls),
    tweets_ls = (tweets_ls - mean(tweets_ls) )/ sd(tweets_ls)
  )

@@

<<spatial selection>>=
physact_base_sem <- errorsarlm(update(base_formula, log_physact ~ .),
                             data = tracts@data, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, log_physact ~ .),
                           data = tracts@data, listw = W, zero.policy = TRUE,
                           type = "mixed")
test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
@

@@

\begin{table*}
  \caption{Estimated Coefficients Relating Park Access to Physical Activity}
  \label{tab:pa_models}
<<pamodelchart, results="asis">>=
pa_models <- list(Base = physact_base_sdm, `Access` = pa_access_sdm,
                       `Access + Tweets` = pa_tweets_sdm)
texreg(pa_models, digits = 4, table = FALSE, single.row = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c("Intercept", termnames, paste("lag", termnames), "$\\rho$",
                             "Access logsum", "lag Access logsum", 
                             "Access + Tweets logsum", "lag Access + Tweets logsum"))
#' screenreg(pa_models, digits = 4, table = FALSE)
@
\end{table*}

@@

<<obesity_models>>=
obese_tweets_sdm <- update(pa_tweets_sdm, log_obesity ~ . + log_physact)
@

@@

\begin{table*}
  \caption{Simulated Impacts of Variables on Obesity}
  \label{tab:obese_impacts}
<<tab:obese_impacts, results="asis">>=
extract_impacts(obese_tweets_sdm) %>%
  group_by(effect) %>%
  transmute(
    term,
    output = paste(round(`estimate`, 5),
                   gtools::stars.pval(`p-val`)),
    order = row_number()
  ) %>%
  spread(effect, output) %>%
  arrange(order) %>%
  dplyr::select(-order) %>%
  mutate(
    term = c(termnames, "Access + Tweets logsum", "log(Physical Activity Rate)")
  ) %>%
  kable("latex", booktabs = T, escape = FALSE, digits = 3, 
        col.names = c("", "Direct", "Indirect", "Total")) %>%
  footnote("$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$", escape = F)
@
\end{table*}

>>>>

tracts@data <-  tbl_df(tracts@data) %>%
  dplyr::transmute(
    geoid = GEOID,
    county_fips = substr(GEOID, 3, 5),
    borough = case_when(
      county_fips == "081" ~ "Queens",
      county_fips == "047" ~ "Brooklyn",
      county_fips == "061" ~ "Manhattan",
      county_fips == "005" ~ "Bronx",
      county_fips == "085" ~ "Staten Island",
      TRUE ~ as.character(NA)
    ),
    obesity = OBESITY,
    physact = 100 - Phys_Act,
    log_obesity = log(OBESITY),
    log_physact = log(100 - Phys_Act),
    density = Pop_Density,
    fulltime = FulltimeWork, college = CollegeDeg,
    single = Single_Percent,
    black = PctBlack, asian = PctAsian, hispanic = PctHispanic,
    other = PctNative + PctPacific,
    Pct0to17, Pct18to29, Pct65plus,
    income = NYC_Income,
    lowincome = Income1 + Income2 + Income3,
    highincome = Income8 + Income9 + Income10
  )
@

@@

<<tractsdata, results="asis", message=FALSE, warning=FALSE, cache=FALSE>>=
tracts_data_index <- data_frame(
  variable =  c(
    "obesity", "physact", "income", "lowincome", "highincome",  
    "density", "fulltime", "college", "single", 
    "Pct0to17", "Pct18to29",  "Pct65plus", "black", "asian", "hispanic", 
    "other")
  ) %>% mutate(order = row_number())

tract_summary <- tracts@data %>%
  dplyr::select(obesity:highincome) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  inner_join(tracts_data_index) %>%
  arrange(order) %>%
  mutate(
    variable = c(
      "Obesity Rate", "Physical Activity Rate",
      "Median tract income",
      "Share of low income",
      "Share of high income",
      "Density: population per square mile",
      "Full-time workers", "College-educated", 
      "Single Adults", "Share of children (0-17)", "Share of young adults (18-29)", 
      "Share of seniors (65+)", "Black population share", "Asian population share", 
      "Hispanic population share", "Other Minorities")
  ) %>%
  dplyr::select(-order)

@@

We predict the rate of physical activity ($y$) in a census tract as a
function of the tract's sociodemographic characteristics and choice-based
accessibility to parks with a semi-log specification:
\begin{equation}\label{eq:themodel}
\log(y_i) = f(\vect{x}_i, CS_i, g(W, \mathit{Obesity}, \vect{X}))
\end{equation}
<<base_formula>>=
base_formula <- formula(
  ~ log(density) +
    lowincome + 
    fulltime + college + single +
    Pct0to17 + Pct18to29 + Pct65plus + # need to leave out a category for collinearity
    black + asian + hispanic + other)

termnames <- c("log(density)" , "log(Income)", 
               "Full-time workers", "College-educated",  "Single Adults", 
               "Share of children (0-17)", "Share of young adults (18-29)", 
               "Share of seniors (65+)", "Black population share", "Asian population share", 
               "Hispanic population share", "Other Minorities")
@
where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
$CS_i$ is a choice-based
accessibility measure for the tract computed from Equation \ref{eq:cs} and
$g(W, \vect{y}, X)$
represents the impact of spatial neighborhood effects on the outcome.

@@

<<distances, warning=FALSE>>=
# calculate centroids of tracts and parks
parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

@@

<<logsum_betas>>=
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-1.79, 0)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.79, 0, 0.1)),
    access_ls = (access_ls - mean(access_ls) )/ sd(access_ls),
    tweets_ls = (tweets_ls - mean(tweets_ls) )/ sd(tweets_ls)
  )

@@

<<spatial selection>>=
physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
                             data = tracts@data, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
                           data = tracts@data, listw = W, zero.policy = TRUE,
                           type = "mixed")
test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
@

@@

\begin{table*}
  \caption{Estimated Coefficients Relating Park Access to Physical Activity}
  \label{tab:pa_models}
<<pamodelchart, results="asis">>=
pa_models <- list(Base = physact_base_sdm, `Access` = pa_access_sdm,
                       `Access + Tweets` = pa_tweets_sdm)
texreg(pa_models, digits = 4, table = FALSE, single.row = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c("Intercept", termnames, "$\\lambda$",
                             "Access logsum", 
                             "Access + Tweets logsum"))
#' screenreg(pa_models, digits = 4, table = FALSE)
@
\end{table*}

@@

<<obesity_models>>=
obese_access_sdm <- update(pa_access_sdm, obesity ~ .)
obese_physact_sdm <- update(obese_access_sdm, . ~ . + physact)
@

@@

\begin{table*}
  \caption{Simulated Impacts of Variables on Obesity}
  \label{tab:obese_impacts}
<<tab:obese_impacts, results="asis">>=
extract_impacts(obese_physact_sdm) %>%
  group_by(effect) %>%
  transmute(
    term,
    output = paste(round(`estimate`, 5),
                   "(",round(`std.error`, 5),")",
                   gtools::stars.pval(`p-val`)),
    order = row_number()
  ) %>%
  spread(effect, output) %>%
  arrange(order) %>%
  dplyr::select(-order) %>%
  mutate(
    term = c(termnames, "Access + Tweets logsum", "log(Physical Activity Rate)")
  ) %>%
  kable("latex", booktabs = T, escape = FALSE, digits = 3, 
        col.names = c("", "Direct", "Indirect", "Total")) %>%
  footnote("$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$", escape = F)
@
\end{table*}

### 2019-01-09 model_estimation.Rmd
WIP

```{r read_tracts}
tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
tracts_sf <- st_read("data/nyc_tracts.geojson", quiet = TRUE) %>%
  st_transform(4326)
```

## Complete Cases
We noticed that our models had different numbers of observations / degrees of 
freedom. Obviously we need to have comparable econometric models. The first thing
we want to look for is missingness in the tracts variables, and which tracts
are missing those variables. The map below shows the tracts that are missing
this information.

```{r tracts_with_missing}
# identify complete cases
complete_tracts_index <- tracts_sf %>%
  st_set_geometry(NULL) %>%
  tbl_df() %>%
  complete.cases()

# make a map of 
leaflet( tracts_sf[!complete_tracts_index, ]) %>%
  addProviderTiles(providers$OpenStreetMap.Mapnik) %>% 
  addPolygons(label = ~ as.character(GEOID))
```

@@

```{r complete_cases}
tracts <- tracts[complete_tracts_index, ]
```

The parks data seems relatively complete, with the exception of a few variables
that are missing everywhere. But we'll ignore this for now.

```{r read_parks, echo=FALSE}
parks <- sf::st_read("data/nyc_parks.geojson")
```

@@

```{r tweettransformation}
parks %>%
  tbl_df() %>%
  dplyr::select(raw = TWEET_COUNT) %>%
  filter(raw < 100) %>%
  mutate(
    `0.5` = yeo.johnson(raw, 0.5),
    `0` = yeo.johnson(raw, 0),
    log = log(raw)
  ) %>%
  gather(lambda, x, -raw) %>%
  ggplot(aes(x = raw, y = x, color = lambda)) + 
  geom_line()

parks <- parks %>%
  mutate(
    log_size = log(Park_Acres),
    log_tweets = yeo.johnson(TWEET_COUNT, 0)
  )

@@

```{r show_data, echo=FALSE}
tracts@data <- tbl_df(tracts@data) %>%
  dplyr::select(
    GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, 
    Income1, Income2, Income3, Income4, Income5, Income6, 
    Income7, Income8, Income9, Income10, Pop_Density, 
    FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, 
    Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific,
    PctOther, PctHispanic
  )  %>%
  mutate(
    log_obesity = log(OBESITY),
    log_physact = log(100 - Phys_Act)
  )

@@

```{r obese_lm, echo=FALSE, message=FALSE, include=FALSE}
base_formula <- formula( 
  ~ log(Pop_Density) + 
    FulltimeWork + CollegeDeg + Single_Percent + 
    Pct0to17 + Pct18to29 + Pct65plus + # need to leave out a category for collinearity  
    PctBlack + PctAsian + PctOther + PctHispanic)
```

@@

```{r spatial selection}
obese_base_lm <- lm(update(base_formula, log_obesity ~ .), data = tracts@data)
obese_base_sar <- lagsarlm(update(base_formula, log_obesity ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE)
obese_base_sem <- errorsarlm(update(base_formula, log_obesity ~ .), 
                             data = tracts@data, listw = W, zero.policy = TRUE)
obese_base_sdm <- lagsarlm(update(base_formula, log_obesity ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE, 
                           type = "mixed")
```

A likelihood ratio test reveals that the SEM is not preferred, so we use the SDM
only going forward.

```{r lrtest}
lmtest::lrtest(obese_base_sem, obese_base_sdm)
```

@@

```{r residuals}
tracts_sf <- tracts_sf[complete_tracts_index, ] %>%
  mutate(
    log_obesity = tracts$log_obesity,  
    obese_base_lm_residuals = obese_base_lm$residuals,
    obese_base_sdm_fitted = obese_base_sdm$fitted.values,  
    obese_base_sdm_residuals = obese_base_sdm$residual
  )

ggplot(tracts_sf, aes(x = log_obesity, y = obese_base_sdm_fitted)) + 
  geom_point()
```

The residuals also appear to be distributed wtihout serious spatial correlation
```{r residuals_map}
pal <- colorQuantile("BrBG", tracts_sf$obese_base_sdm_residuals, n = 9)
leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(color = ~pal(obese_base_sdm_residuals), stroke = NA, opacity = 0.8)
```

@@

Consider that an individual is choosing a park for a recreation activity.
According to basic choice theory (Mcfadden 1974), the probability of choosing
park $p$ from the set of all regional parks $J$ is:

$$ P(p | V_p) = \frac{\exp(V_p)}{\sum_{j \in J}\exp(V_j)}$$
where parks are differentiated from each other by their relative measurable
utilitie $V$. In principle, $V$ may include any measurable attributes of either
the choice maker or the park. In this study we use a linear formulation of

$$V_{ij} = size_j\beta_s + distance_{ij}\beta_d$$
incorporating the size of the park in acres and the distance of the park from
the census tract $i$ in miles. The coefficients $\beta$ are typically estimated from 
surveys, though in the absence of a survey we apply a maximum likelihood
technique described below.

A key theoretical understanding of random utility choice models is that the
consumer surplus of the choice set can be otained as the log-sum of the
denominator of the choice probability equation. In plainer terms, the *total value*
of an individual's park accessibility is defined to be:

$$CS_i = \ln\left({\sum_{j \in J}\exp(V_{ij})}\right)$$

There are several advantages to a log-sum defined metric relative to
buffer-based accessibility metrics more commonly found in the literature. First,
all individuals are defined as having some access to all parks, rather than an
arbitrary limit of 1/2 mile or so. This allows for the fact that some people are
more or less sensitive to distances, and that distance is a continuous, and not
a binary, phenomenon. Second, the random utility formulation allows the
researcher to include any attribute of the park; in this case, we consider the
size of the park as an element of accessibility. This suggests that not all
parks are equal, and that a large park such as New York City's Central Park may
provide health and activity benefits over a much larger area than a smaller
community square.

McFadden, D. (1974). The measurement of urban travel demand. Journal of public economics, 3(4), 303-328.

In the absence of a park choice survey, we estimated likely values of the $\beta$ 
coefficients by iteratively searching for the values which produced the highest
model likelihood in *which model did we use to estimate likelihood?*. The search
was constrained by two assertions. First, we required that the coefficient on
size be positive and that on distance negative; all else equal, people will
prefer to use larger parks that are nearer to their residence. Second, we visually
inspected the resulting accessibility scores to ensure that the scores produced a 
reasonably varied pattern of access throughout the metropolitan region.

@@

First, we calculate the distance between the tracts and the parks.
```{r distancematrix}
# calculate centroids of tracts and parks
tract_centroids <- tracts %>% st_as_sf() %>% st_centroid() 
park_centroids <- parks %>% st_centroid() %>% st_transform(st_crs(tract_centroids))

# distances from all tracts to all zones
distances <- st_distance(tract_centroids, park_centroids, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()
```

```{r show_accessibility}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-0.8, 0.8)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.8, 0.8, 0.2))
  )

@@

leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(group = "access", color = ~pal(access_ls)) %>%
  addPolygons(group = "access + tweets", color = ~pal(tweets_ls)) %>%
  addLayersControl(baseGroups = c("access", "access + tweets"))

@@

```{r obesity_access_models}
access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
```

```{r modelchart}
obesity_models <- list(Base = obese_base_sdm, `Access` = access_sdm, 
                       `Access + Tweets` = tweets_sdm)
screenreg(obesity_models, digits = 4)
```

>>>>

## Complete Cases
We noticed that our models had different numbers of observations / degrees of 
freedom. Obviously we need to have comparable econometric models. The first thing
we want to look for is missingness in the tracts variables, and which tracts
are missing those variables. The map below shows the tracts that are missing
this information.
```{r read_tracts}
tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
tracts_sf <- st_read("data/nyc_tracts.geojson")

# identify complete cases
complete_tracts_index <- tracts@data %>%
  tbl_df() %>%
  complete.cases()
tracts <- tracts[complete_tracts_index, ]

tracts@data <-  tbl_df(tracts@data) %>%
  dplyr::transmute(
    geoid = GEOID,
    county_fips = substr(GEOID, 3, 5),
    borough = case_when(
      county_fips == "081" ~ "Queens",
      county_fips == "047" ~ "Brooklyn",
      county_fips == "061" ~ "Manhattan",
      county_fips == "005" ~ "Bronx",
      county_fips == "085" ~ "Staten Island",
      TRUE ~ as.character(NA)
    ),
    obesity = OBESITY,
    physact = 100 - Phys_Act,
    log_obesity = log(OBESITY),
    log_physact = log(100 - Phys_Act),
    density = Pop_Density,
    fulltime = FulltimeWork, college = CollegeDeg,
    single = Single_Percent,
    black = PctBlack, asian = PctAsian, hispanic = PctHispanic,
    other = PctNative + PctPacific,
    Pct0to17, Pct18to29, Pct65plus,
    income = NYC_Income
  )
```

```{r tracts_with_missing}
# make a map of 
leaflet( tracts_sf[!complete_tracts_index, ] %>% st_transform(4326)) %>%
  addProviderTiles(providers$OpenStreetMap.Mapnik) %>% 
  addPolygons(label = ~ as.character(GEOID))
```

@@

The parks data seems relatively complete, with the exception of a few variables
that are missing everywhere. Also it seems that we are including parking strips 
very small pieces of property, even though these facilities are unlikely to 
generate physical activity - related trips. Finally, sports fields within larger
parks probably do not need to be double-counted.

```{r read_parks, echo=FALSE}
allparks <- sf::st_read("data/nyc_parks.geojson", quiet = TRUE) %>%
  transmute(
    size = Park_Acres,
    log_size = log(Park_Acres),
    tweets = TWEET_COUNT,
    log_tweets = yeo.johnson(TWEET_COUNT, 0)
  )

parks <- allparks %>%
  filter(size > 0.5)
```

The map below shows the parks we are including.
```{r parksmap}
leaflet( allparks %>% filter(size > 0.5) %>% st_transform(4326)) %>%
  addProviderTiles(providers$OpenStreetMap.Mapnik) %>% 
  addPolygons()
```

@@

```{r tweettransformation}
data_frame(x = seq(0, 50, by = 0.5)) %>% 
  mutate(log = log(x), `yeo-johnson` = yeo.johnson(x, 0)) %>%
  gather(transform, y, -x) %>%
  ggplot(aes(x = x, y = y, color= transform)) + geom_line()

@@

```{r show_data, echo=FALSE}
tracts@data
```

@@

```{r obese_lm, echo=FALSE, message=FALSE, include=FALSE}
base_formula <- formula(
  ~ log(density) + log(income) +
    fulltime + college + single +
    Pct0to17 + Pct18to29 + Pct65plus + # need to leave out a category for collinearity
    black + asian + hispanic + other)
```

@@

```{r spatial selection}
physact_base_lm <- lm(update(base_formula, physact ~ .), data = tracts)
physact_base_sar <- lagsarlm(update(base_formula, physact ~ .),
                           data = tracts@data, listw = W, zero.policy = TRUE)
physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
                             data = tracts@data, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
                           data = tracts@data, listw = W, zero.policy = TRUE,
                           type = "mixed")
test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
```

A likelihood ratio test reveals that the SEM actually preferred, so we use this
only going forward.

```{r }
physact_models <- list("OLS" = physact_base_lm, "SAR" = physact_base_sar, 
                       "SEM" = physact_base_sem, "SDM" = physact_base_sdm)
screenreg(physact_models, digits = 5)

@@

```{r residuals}
tracts_sf <- tracts_sf %>%
  mutate(
    log_obesity = tracts$log_physact,  
    physact_base_lm_residuals = physact_base_lm$residuals,
    physact_base_sem_fitted = physact_base_sem$fitted.values,  
    physact_base_sem_residuals = physact_base_sem$residual
  )

ggplot(tracts_sf, aes(x = log_obesity, y = physact_base_sem_fitted)) + 
  geom_point()
```

The residuals also appear to be distributed wtihout serious spatial correlation
```{r residuals_map}
pal <- colorQuantile("BrBG", tracts_sf$physact_base_sem_residuals, n = 9)
leaflet(tracts_sf %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(color = ~pal(physact_base_sem_residuals), stroke = NA, opacity = 0.8)
```

@@

@@

First, we calculate the distance between the tracts and the parks.
```{r distancematrix}
# calculate centroids of tracts and parks
parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

# distances from all tracts to all zones
distances <- st_distance(pop_weighted_centroids, parks, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()

# assert that a tract must be at least 1/10 mile from a park
distances <- pmax(distances, 0.1)
```

We now need to run a subroutine to determine the values of the beta coefficients
which produce the highest model likelihood, and .

```{r notweets_logsum, eval = FALSE}
notweets_logsum <- function(betas, distances, parks, tracts, model) {

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$log_size,
    betas = betas)

  tracts@data$access_ls <- (logsum - mean(logsum)) / sd(logsum)

  sdm <- update(model, . ~ . + access_ls)
  return(-logLik(sdm))
}

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-0.42, 0.5), # distance, size 
  lower = c(-10, 0), # size coefficient must be positive 
  upper = c(0, 10), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = physact_base_sem,
  method = "L-BFGS-B", 
  control = list(trace = 6))
```

```{r tweets_logsum, eval = FALSE}
tweets_logsum <- function(betas, distances, parks, tracts, model) {

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$log_size, tweets = parks$log_tweets,
    betas = betas)

  tracts@data$tweets_ls <- (logsum - mean(logsum)) / sd(logsum)

  sdm <- update(model, . ~ . + tweets_ls)
  return(-logLik(sdm))
}

tweets_sdm_val <- optim(
  fn = tweets_logsum,  
  par = c(-0.42, 0.5, 1), # distance, size 
  lower = c(-10, 0, -10), # size coefficient must be positive 
  upper = c(0, 10, 10), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = physact_base_sem,
  method = "L-BFGS-B", 
  control = list(trace = 6))

```{r show_accessibility}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-1.796, 1.0)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-1.796, 1.0, 0.1)),
    access_ls = (access_ls - mean(access_ls) )/ sd(access_ls),
    tweets_ls = (tweets_ls - mean(tweets_ls) )/ sd(tweets_ls)
  )

@@

leaflet(tracts_sf %>% st_transform(4326)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(group = "access", color = ~pal(access_ls)) %>%
  addPolygons(group = "access + tweets", color = ~pal(tweets_ls)) %>%
  addLayersControl(baseGroups = c("access", "access + tweets"))

@@

```{r obesity_access_models}
access_sem <- update(physact_base_sem, .~ . + access_ls)
tweets_sem <- update(physact_base_sem, .~ . + tweets_ls)
```

```{r modelchart}
physact_models <-  
screenreg()
